---
title: "R Notebook"
output: html_notebook
---

# Set Global Variables here

```{r}
# Please change the working directory
Working_dir <- "~/Desktop/AVATAR/PADIT-seq-Manuscript/Code_Availability_Revision/"

# Please be sure to install these libraries
library(pheatmap); library(ggplot2); library(DESeq2); library(ggrepel); library("stringr")

# FDR cutoff (do not change)
Cutoff_Value <- 0.05
```


# Custom functions
```{r}
library(seqLogo)

# Function to generate PWM logo for any specified k-mers
Generate_PWM_seqlogo <- function(kmers_vec, kmer_length = 8)
{
  # Generate data frame for seqlogo
  kmers_vec_df <- data.frame()
  for(i in 1:kmer_length)
  {
    letter_i <- substr(kmers_vec, i, i)
    count <- 0
    for(j in c("A", "C", "G", "T"))
    {
      count <- count + 1
      kmers_vec_df[i, count] <- sum(letter_i == j)
    }
  }
  colnames(kmers_vec_df) <- c("A", "C", "G", "T")
  
  #define function that divides the frequency by the row sum i.e. proportions
  proportion <- function(x){
     rs <- sum(x);
     return(x / rs);
  }
   
  #create position weight matrix
  NKX2.5_seqlogo <- apply(kmers_vec_df, 1, proportion)
  NKX2.5_seqlogo <- makePWM(NKX2.5_seqlogo)
  seqLogo(NKX2.5_seqlogo)
}

```



# Obtain NKX2.5 8-mer PADIT-seq log2foldchange values from 10-mer data
# Caution: This is going to take a while (approximately 3 hours)

```{r}
# # Read NKX2.5 PADIT-seq data
# dds_results_NKX2.5_df <- read.table(paste(paste(Working_dir, "Output_Files", sep = "/"), "dds_results_NKX2.5_df.txt", sep = "/"), header = TRUE)
# dds_results_NKX2.5_df <- dds_results_NKX2.5_df[complete.cases(dds_results_NKX2.5_df), ]
# dds_results_NKX2.5_df$TFBS <- rownames(dds_results_NKX2.5_df)
# 
# # Read NKX2.5 PBM data
# NKX2.5_PBM_Escores <- read.table(paste(paste(Working_dir, "Input_Files/PBM_data_NKX2-5", sep = "/"), "NKX2.5_REF_R2_8mers_11111111.txt", sep = "/"), header = TRUE)
# 
# # 
# for(k in 0:2) # The 3 8-mers overlapping each 10-mer
# {
#   NKX2.5_PBM_Escores_PADIT <- data.frame()
#   for(i in 1:nrow(NKX2.5_PBM_Escores)) # For each register, calculate the median 8-mer scores
#   {
#     Current_8mers <- NKX2.5_PBM_Escores[i,] 
#     
#     # Forward orientation
#     Fwd <- dds_results_NKX2.5_df[which(substr(dds_results_NKX2.5_df$TFBS, k+1, k+8) == Current_8mers$X8.mer[1]),]
#     Fwd.tmp <- Fwd[order(Fwd$log2FoldChange, decreasing = TRUE),]
#     Fwd <- Fwd.tmp; rm(Fwd.tmp)
#     if(nrow(Fwd) > 0)
#     {
#       Fwd_subset <- Fwd[ceiling(nrow(Fwd)/2), c("baseMean", "log2FoldChange", "padj", "MPRAactivity")] # Obtain median
#     }
#     else
#     {
#       Fwd_subset <- as.data.frame(t(c(0, -100, 1, 0))) 
#       colnames(Fwd_subset) <- c("baseMean", "log2FoldChange", "padj", "MPRAactivity")
#     }
#     
#     # Reverse complement
#     Rev <- dds_results_NKX2.5_df[which(substr(dds_results_NKX2.5_df$TFBS, k+1, k+8) == Current_8mers$X8.mer.1[1]),]
#     Rev.tmp <- Rev[order(Rev$log2FoldChange, decreasing = TRUE),]
#     Rev <- Rev.tmp; rm(Rev.tmp)
#     if(nrow(Rev) > 0)
#     {
#       Rev_subset <- Rev[ceiling(nrow(Rev)/2), c("baseMean", "log2FoldChange", "padj", "MPRAactivity")] # Obtain median
#     }
#     else
#     {
#       Rev_subset <- as.data.frame(t(c(0, -100, 1, 0)))
#       colnames(Rev_subset) <- c("baseMean", "log2FoldChange", "padj", "MPRAactivity")
#     }
#     
#     # Keep orientation with the higher value
#     if((Fwd_subset$log2FoldChange >= Rev_subset$log2FoldChange) | (nrow(Rev_subset) == 0))
#     {
#       Current_8mers <- cbind(Current_8mers, Fwd_subset)
#     }
#     if((Fwd_subset$log2FoldChange < Rev_subset$log2FoldChange) | (nrow(Fwd_subset) == 0))
#     {
#       Current_8mers <- cbind(Current_8mers, Rev_subset)
#     }
#     
#     # Add to the growing DF
#     NKX2.5_PBM_Escores_PADIT <- rbind(NKX2.5_PBM_Escores_PADIT, Current_8mers)
#   
#     # remove all the variable in current iteration
#     variables_to_remove = c("Current_8mers", "Fwd", "Fwd_subset", "Rev", "Rev_subset")
#     for (var_name in variables_to_remove)
#     {
#       if (exists(var_name))
#       {
#         rm(list=var_name)
#       }
#     }
#   }
#   
#   # Store the files
#   if(k == 0){ write.table(NKX2.5_PBM_Escores_PADIT, file = paste(paste(Working_dir, "Output_Files/Median_kmer_log2FC", sep = "/"), "NKX2.5_all8mers_1_8_median.txt", sep = "/"), col.names = TRUE, row.names = FALSE, quote = FALSE, sep = "\t") }
#   if(k == 1){ write.table(NKX2.5_PBM_Escores_PADIT, file = paste(paste(Working_dir, "Output_Files/Median_kmer_log2FC", sep = "/"), "NKX2.5_all8mers_2_9_median.txt", sep = "/"), col.names = TRUE, row.names = FALSE, quote = FALSE, sep = "\t") }
#   if(k == 2){ write.table(NKX2.5_PBM_Escores_PADIT, file = paste(paste(Working_dir, "Output_Files/Median_kmer_log2FC", sep = "/"), "NKX2.5_all8mers_3_10_median.txt", sep = "/"), col.names = TRUE, row.names = FALSE, quote = FALSE, sep = "\t") }
# }

```


# Plot comparison to PBM E-scores
```{r}
# Read NKX2.5 PBM data
NKX2.5_PBM_Escores <- read.table(paste(paste(Working_dir, "Input_Files/PBM_data_NKX2-5", sep = "/"), "NKX2-5_anti-GST_rep1_primary_8mers_11111111.txt", sep = "/"), header = TRUE)

# Read NKX2.5 8-mer PADIT-seq log2foldchange values for the 3 registers
Register_1_8 <- read.table(paste(paste(Working_dir, "Output_Files/Median_kmer_log2FC", sep = "/"), "NKX2.5_all8mers_1_8_median.txt", sep = "/"), header = TRUE)
Register_2_9 <- read.table(paste(paste(Working_dir, "Output_Files/Median_kmer_log2FC", sep = "/"), "NKX2.5_all8mers_2_9_median.txt", sep = "/"), header = TRUE)
Register_3_10 <- read.table(paste(paste(Working_dir, "Output_Files/Median_kmer_log2FC", sep = "/"), "NKX2.5_all8mers_3_10_median.txt", sep = "/"), header = TRUE)

# Re-define MPRAactivity
Register_1_8$MPRAactivity <- (Register_1_8$log2FoldChange > 0 & Register_1_8$padj < Cutoff_Value)*1
Register_2_9$MPRAactivity <- (Register_2_9$log2FoldChange > 0 & Register_2_9$padj < Cutoff_Value)*1
Register_3_10$MPRAactivity <- (Register_3_10$log2FoldChange > 0 & Register_3_10$padj < Cutoff_Value)*1

# Number of red points?
table(Register_1_8$MPRAactivity)
table(Register_2_9$MPRAactivity)
table(Register_3_10$MPRAactivity)

# Fraction of red points?
sum((Register_1_8$MPRAactivity == 1)*1)/nrow(Register_1_8)
sum((Register_2_9$MPRAactivity == 1)*1)/nrow(Register_2_9)
sum((Register_3_10$MPRAactivity == 1)*1)/nrow(Register_3_10)

################################################################# Average of all 3 registers
# Format
colnames(Register_1_8) <- paste(colnames(Register_1_8), "1_8", sep = "_")
colnames(Register_2_9) <- paste(colnames(Register_2_9), "2_9", sep = "_")
colnames(Register_3_10) <- paste(colnames(Register_3_10), "3_10", sep = "_")
TEMP1 <- merge(Register_1_8, Register_2_9, 
               by.x = "X8.mer_1_8", by.y = "X8.mer_2_9")
TEMP2 <- merge(TEMP1, Register_3_10, 
               by.x = "X8.mer_1_8", by.y = "X8.mer_3_10")
NKX2.5_PBM_Escores_PADIT <- TEMP2; rm(TEMP1); rm(TEMP2)

# Define Median values
NKX2.5_PBM_Escores_PADIT$Median_baseMean <- apply(NKX2.5_PBM_Escores_PADIT[,c("baseMean_1_8", "baseMean_2_9", "baseMean_3_10")], 1, median)
NKX2.5_PBM_Escores_PADIT$Mean_log2FC <- apply(NKX2.5_PBM_Escores_PADIT[,c("log2FoldChange_1_8", "log2FoldChange_2_9", "log2FoldChange_3_10")], 1, median)
NKX2.5_PBM_Escores_PADIT$padj <- apply(NKX2.5_PBM_Escores_PADIT[,c("padj_1_8", "padj_2_9", "padj_3_10")], 1, median)
NKX2.5_PBM_Escores_PADIT$MPRAactivity <- apply(NKX2.5_PBM_Escores_PADIT[,c("MPRAactivity_1_8", "MPRAactivity_2_9", "MPRAactivity_3_10")], 1, median)

# Add PBM E-scores and Z-scores
TEMP <- merge(NKX2.5_PBM_Escores, NKX2.5_PBM_Escores_PADIT, 
              by.x = "X8.mer", by.y = "X8.mer_1_8")
NKX2.5_PBM_Escores_PADIT <- TEMP; rm(TEMP)

# Define colours
NKX2.5_PBM_Escores_PADIT$Colour <- "black"
NKX2.5_PBM_Escores_PADIT$Colour[which(NKX2.5_PBM_Escores_PADIT$MPRAactivity == 1)] <- "red"

# Plot (against e-scores)
NKX2.5_PBM_Escores_PADIT_subset <- NKX2.5_PBM_Escores_PADIT[which(NKX2.5_PBM_Escores_PADIT$Median_baseMean > 5), ]
plot(NKX2.5_PBM_Escores_PADIT_subset$E.score[which(NKX2.5_PBM_Escores_PADIT_subset$Colour == "black")], 
     NKX2.5_PBM_Escores_PADIT_subset$Mean_log2FC[which(NKX2.5_PBM_Escores_PADIT_subset$Colour == "black")], 
     cex = 0.5, pch = 19, cex.axis = 2, cex.lab = 2,
     col = "black", 
     xlim = c(-0.45, 0.5), ylim = c(-0.5, 3.8), 
     xlab = "E-score", ylab = "PADIT-seq log2 (ALFA-NKX2.5 / No-DBD)")
points(NKX2.5_PBM_Escores_PADIT_subset$E.score[which(NKX2.5_PBM_Escores_PADIT_subset$Colour == "red")], 
       NKX2.5_PBM_Escores_PADIT_subset$Mean_log2FC[which(NKX2.5_PBM_Escores_PADIT_subset$Colour == "red")],
       cex = 0.5, pch = 19, col = "red")
abline(h = 0, col = "red")
table(NKX2.5_PBM_Escores_PADIT_subset$Colour)
cor.test(NKX2.5_PBM_Escores_PADIT_subset$E.score, NKX2.5_PBM_Escores_PADIT_subset$Mean_log2FC)

# Plot (against z-scores)
NKX2.5_PBM_Escores_PADIT_subset <- NKX2.5_PBM_Escores_PADIT[which(NKX2.5_PBM_Escores_PADIT$Median_baseMean > 5), ]
plot(NKX2.5_PBM_Escores_PADIT_subset$Z.score[which(NKX2.5_PBM_Escores_PADIT_subset$Colour == "black")], 
     NKX2.5_PBM_Escores_PADIT_subset$Mean_log2FC[which(NKX2.5_PBM_Escores_PADIT_subset$Colour == "black")], 
     cex = 0.5, pch = 19, cex.axis = 2, cex.lab = 2,
     col = "black", 
     xlim = c(-3, 20), ylim = c(-0.5, 3.8), 
     xlab = "Z-score", ylab = "PADIT-seq log2 (ALFA-NKX2.5 / No-DBD)")
points(NKX2.5_PBM_Escores_PADIT_subset$Z.score[which(NKX2.5_PBM_Escores_PADIT_subset$Colour == "red")], 
       NKX2.5_PBM_Escores_PADIT_subset$Mean_log2FC[which(NKX2.5_PBM_Escores_PADIT_subset$Colour == "red")],
       cex = 0.5, pch = 19, col = "red")
abline(h = 0, col = "red")
cor.test(NKX2.5_PBM_Escores_PADIT_subset$Z.score, NKX2.5_PBM_Escores_PADIT_subset$Mean_log2FC)

```



#################################################################################################### Add HT-SELEX, ProBound and FIMO data for AUROC analysis
################################################## Add HT-SELEX data
```{r}
################################################## Read HT-SELEX data
# Read HT-SELEX enriched 8-mers
table_1 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_NKX2-5", sep = "/"), "NKX2-5_HT-SELEX_Cycle1_enriched_8mers.txt", sep = "/"), header = TRUE)
table_2 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_NKX2-5", sep = "/"), "NKX2-5_HT-SELEX_Cycle2_enriched_8mers.txt", sep = "/"), header = TRUE)
table_3 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_NKX2-5", sep = "/"), "NKX2-5_HT-SELEX_Cycle3_enriched_8mers.txt", sep = "/"), header = TRUE)
table_4 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_NKX2-5", sep = "/"), "NKX2-5_HT-SELEX_Cycle4_enriched_8mers.txt", sep = "/"), header = TRUE)

# Calculate Observed / Expected Ratio
table_1$Cycle1 <- table_1$ObservedCount/table_1$ExpectedCount
table_2$Cycle2 <- table_2$ObservedCount/table_2$ExpectedCount
table_3$Cycle3 <- table_3$ObservedCount/table_3$ExpectedCount
table_4$Cycle4 <- table_4$ObservedCount/table_4$ExpectedCount

# merge -1 
table_1 <- table_1[, c("Kmer", "Cycle1")]
table_2 <- table_2[, c("Kmer", "Cycle2")]
table_3 <- table_3[, c("Kmer", "Cycle3")]
table_4 <- table_4[, c("Kmer", "Cycle4")]
HT_SELEX <- merge(merge(merge(table_1, table_2, by = "Kmer"), table_3, by = "Kmer"), table_4, by = "Kmer")

# merge -2
TEMP1 <- merge(NKX2.5_PBM_Escores_PADIT, HT_SELEX, by.x = "X8.mer", by.y = "Kmer", all.x = TRUE)
TEMP2 <- merge(TEMP1, HT_SELEX, by.x = "X8.mer.1", by.y = "Kmer",  all.x = TRUE)
TEMP2[is.na(TEMP2)] <- 0

# Keep orientation that is larger
TEMP2$Cycle1 <- apply(TEMP2[, c("Cycle1.x", "Cycle1.y")], 1, max)
TEMP2$Cycle2 <- apply(TEMP2[, c("Cycle2.x", "Cycle2.y")], 1, max)
TEMP2$Cycle3 <- apply(TEMP2[, c("Cycle3.x", "Cycle3.y")], 1, max)
TEMP2$Cycle4 <- apply(TEMP2[, c("Cycle4.x", "Cycle4.y")], 1, max)
NKX2.5_PBM_Escores_PADIT_HTSELEX <- TEMP2[, which(!colnames(TEMP2) %in% c("Cycle1.x", "Cycle1.y", "Cycle2.x", "Cycle2.y", "Cycle3.x", "Cycle3.y", "Cycle4.x", "Cycle4.y"))]
```




################################################## Add ProBound data
```{r}
################################################## Read ProBound data
# _NNNN
All8mers_1 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_NKX2-5/ProBound", sep = "/"), "All_8mers__NNNN_ProBound.txt", sep = "/"), header = FALSE)
colnames(All8mers_1) <- c("kmer", "rel_affinity1")

# N_NNNN
All8mers_2 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_NKX2-5/ProBound", sep = "/"), "All_8mers_N_NNN_ProBound.txt", sep = "/"), header = FALSE)
colnames(All8mers_2) <- c("kmer", "rel_affinity2")

# NN_NNN
All8mers_3 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_NKX2-5/ProBound", sep = "/"), "All_8mers_NN_NN_ProBound.txt", sep = "/"), header = FALSE)
colnames(All8mers_3) <- c("kmer", "rel_affinity3")

# NNN_N
All8mers_4 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_NKX2-5/ProBound", sep = "/"), "All_8mers_NNN_N_ProBound.txt", sep = "/"), header = FALSE)
colnames(All8mers_4) <- c("kmer", "rel_affinity4")

# NNNN_
All8mers_5 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_NKX2-5/ProBound", sep = "/"), "All_8mers_NNNN__ProBound.txt", sep = "/"), header = FALSE)
colnames(All8mers_5) <- c("kmer", "rel_affinity5")

### Merge
All8mers <- All8mers_1
All8mers$rel_affinity2 <- All8mers_2$rel_affinity2
All8mers$rel_affinity3 <- All8mers_3$rel_affinity3
All8mers$rel_affinity4 <- All8mers_4$rel_affinity4
All8mers$rel_affinity5 <- All8mers_5$rel_affinity5
All8mers$trimmed_kmer <- substr(All8mers$kmer, 1, 8)
All8mers$rel_affinity <- apply(All8mers[, paste("rel_affinity", 1:5, sep = "")], 1, max)
ProBound_results <- All8mers[, c("trimmed_kmer", "rel_affinity")]

# Merge
TEMP1 <- merge(NKX2.5_PBM_Escores_PADIT_HTSELEX, ProBound_results, 
               by.x = "X8.mer", by.y = "trimmed_kmer")
TEMP2 <- merge(TEMP1, ProBound_results, 
               by.x = "X8.mer.1", by.y = "trimmed_kmer")
NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound <- TEMP2
NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound$log2_rel_affinity <- log2(apply(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound[, c("rel_affinity.x", "rel_affinity.y")], 1, max))
NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound <- NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound[, which(!colnames(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound) %in% c("rel_affinity.x", "rel_affinity.y"))]

################################################## Add FIMO data
PWM_FIMO <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_NKX2-5/FIMO", sep = "/"), "All_8mers.Match.MA0063.1.txt", sep = "/"), header = FALSE)[, c(1, 8)]
colnames(PWM_FIMO) <- c("sequence_name", "FIMO.p.value")

### Merge-2
TEMP1 <- merge(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound, PWM_FIMO, 
               by.x = "X8.mer", by.y = "sequence_name")
TEMP2 <- merge(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound, PWM_FIMO, 
               by.x = "X8.mer.1", by.y = "sequence_name")
TEMP3 <- unique(rbind(TEMP1, TEMP2))
NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO <- TEMP3
NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$FIMO.p.value <- -log10(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$FIMO.p.value)

```




################################################## Plot AUROC
```{r}
library("DescTools")
Columns_To_Plot <- c("E.score", "Cycle1", "Cycle2", "Cycle3", "Cycle4", "log2_rel_affinity", "FIMO.p.value")
# Columns_To_Plot <- c("E.score", "Z.score")
for(k in 1:length(Columns_To_Plot))
{
  thresholds <- seq(min(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO[, Columns_To_Plot[k]]), 
                    max(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO[, Columns_To_Plot[k]]), length.out = 5000)
  fraction_red <- vector()
  fraction_black <- vector()
  for(i in 1:length(thresholds))
  {
    NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$AboveThreshold <- (NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO[, Columns_To_Plot[k]] > thresholds[i])*1
    fraction_red[i] <- nrow(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO[which(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$MPRAactivity == 1 & NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$AboveThreshold == 1),])
    fraction_black[i] <- nrow(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO[which(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$MPRAactivity != 1 & NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$AboveThreshold == 1),])
  }
  
  # print AUC
  # print AUC
  DF <- cbind(xvalues = fraction_black/(nrow(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO) - sum(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$MPRAactivity)), 
              yvalues = fraction_red/sum(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$MPRAactivity))
  DF <- as.data.frame(DF)
  DF <- DF[order(DF$xvalues, decreasing = FALSE),]
  DF <- rbind(DF, c(1, 1))
  print(AUC(DF$xvalues, DF$yvalues))
  
  # plot
  if(k == 1)
  {
    # Plot AUC curve
    plot(fraction_black/(nrow(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO) - sum(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$MPRAactivity)), 
         fraction_red/sum(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$MPRAactivity), 
         type = "l", col = "black")
    abline(a = 0, b = 1, col = "black")
  }
  if(k > 1 & k < 6)
  {
    # Plot AUC curve
    points(fraction_black/(nrow(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO) - sum(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$MPRAactivity)), 
         fraction_red/sum(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$MPRAactivity), 
         type = "l", col = "cyan3")
  }
  if(k == 6)
  {
    # Plot AUC curve
    points(fraction_black/(nrow(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO) - sum(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$MPRAactivity)), 
         fraction_red/sum(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$MPRAactivity), 
         type = "l", col = "red")
  }
  if(k == 7)
  {
    # Plot AUC curve
    points(fraction_black/(nrow(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO) - sum(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$MPRAactivity)), 
         fraction_red/sum(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$MPRAactivity), 
         type = "l", col = "green")
  }
}

```



# Specificity versus Sensitivity of HT-SELEX data
```{r}
# Observed versus Expected threshold
ratio_threshold <- 3

# Define the active 8-mers
NKX2.5_PBM_Escores_PADIT_sig8mers <- c(NKX2.5_PBM_Escores_PADIT$X8.mer[which(NKX2.5_PBM_Escores_PADIT$MPRAactivity == 1)], 
                                       NKX2.5_PBM_Escores_PADIT$X8.mer.1[which(NKX2.5_PBM_Escores_PADIT$MPRAactivity == 1)])
NKX2.5_PBM_Escores_PADIT_sig8mers <- unique(NKX2.5_PBM_Escores_PADIT_sig8mers)

# Read HT-SELEX enriched 8-mers
table_1 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_NKX2-5", sep = "/"), "NKX2-5_HT-SELEX_Cycle1_enriched_8mers_DefaultParameters.txt", sep = "/"), header = TRUE)
table_2 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_NKX2-5", sep = "/"), "NKX2-5_HT-SELEX_Cycle2_enriched_8mers_DefaultParameters.txt", sep = "/"), header = TRUE)
table_3 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_NKX2-5", sep = "/"), "NKX2-5_HT-SELEX_Cycle3_enriched_8mers_DefaultParameters.txt", sep = "/"), header = TRUE)
table_4 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_NKX2-5", sep = "/"), "NKX2-5_HT-SELEX_Cycle4_enriched_8mers_DefaultParameters.txt", sep = "/"), header = TRUE)

# filter
table_1 <- table_1[which(table_1$ObservedCount/table_1$ExpectedCount > ratio_threshold),]
table_2 <- table_2[which(table_2$ObservedCount/table_2$ExpectedCount > ratio_threshold),]
table_3 <- table_3[which(table_3$ObservedCount/table_3$ExpectedCount > ratio_threshold),]
table_4 <- table_4[which(table_4$ObservedCount/table_4$ExpectedCount > ratio_threshold),]

# Add relevant columns
NKX2.5_PBM_Escores_PADIT$Cycle1 <- (NKX2.5_PBM_Escores_PADIT$X8.mer %in% table_1$Kmer | NKX2.5_PBM_Escores_PADIT$X8.mer.1 %in% table_1$Kmer) 
NKX2.5_PBM_Escores_PADIT$Cycle2 <- (NKX2.5_PBM_Escores_PADIT$X8.mer %in% table_2$Kmer | NKX2.5_PBM_Escores_PADIT$X8.mer.1 %in% table_2$Kmer) 
NKX2.5_PBM_Escores_PADIT$Cycle3 <- (NKX2.5_PBM_Escores_PADIT$X8.mer %in% table_3$Kmer | NKX2.5_PBM_Escores_PADIT$X8.mer.1 %in% table_3$Kmer) 
NKX2.5_PBM_Escores_PADIT$Cycle4 <- (NKX2.5_PBM_Escores_PADIT$X8.mer %in% table_4$Kmer | NKX2.5_PBM_Escores_PADIT$X8.mer.1 %in% table_4$Kmer) 

# Number of rows
num_enriched_HTSELEX <- c(sum(NKX2.5_PBM_Escores_PADIT$Cycle1), 
                          sum(NKX2.5_PBM_Escores_PADIT$Cycle2), 
                          sum(NKX2.5_PBM_Escores_PADIT$Cycle3), 
                          sum(NKX2.5_PBM_Escores_PADIT$Cycle4))

# Specificity (red)
vec1 <- c(nrow(NKX2.5_PBM_Escores_PADIT[which(NKX2.5_PBM_Escores_PADIT$Cycle1 == 1 & NKX2.5_PBM_Escores_PADIT$MPRAactivity == 1),]),
          nrow(NKX2.5_PBM_Escores_PADIT[which(NKX2.5_PBM_Escores_PADIT$Cycle2 == 1 & NKX2.5_PBM_Escores_PADIT$MPRAactivity == 1),]),
          nrow(NKX2.5_PBM_Escores_PADIT[which(NKX2.5_PBM_Escores_PADIT$Cycle3 == 1 & NKX2.5_PBM_Escores_PADIT$MPRAactivity == 1),]),
          nrow(NKX2.5_PBM_Escores_PADIT[which(NKX2.5_PBM_Escores_PADIT$Cycle4 == 1 & NKX2.5_PBM_Escores_PADIT$MPRAactivity == 1),]))
vec1 <- vec1/num_enriched_HTSELEX

# Sensitivity (blue)
vec2 <- c(nrow(NKX2.5_PBM_Escores_PADIT[which(NKX2.5_PBM_Escores_PADIT$Cycle1 == 1 & NKX2.5_PBM_Escores_PADIT$MPRAactivity == 1),]),
          nrow(NKX2.5_PBM_Escores_PADIT[which(NKX2.5_PBM_Escores_PADIT$Cycle2 == 1 & NKX2.5_PBM_Escores_PADIT$MPRAactivity == 1),]),
          nrow(NKX2.5_PBM_Escores_PADIT[which(NKX2.5_PBM_Escores_PADIT$Cycle3 == 1 & NKX2.5_PBM_Escores_PADIT$MPRAactivity == 1),]),
          nrow(NKX2.5_PBM_Escores_PADIT[which(NKX2.5_PBM_Escores_PADIT$Cycle4 == 1 & NKX2.5_PBM_Escores_PADIT$MPRAactivity == 1),]))
vec2 <- vec2/length(NKX2.5_PBM_Escores_PADIT_sig8mers)

# 
plot(1:4, vec1, type = "b", pch = 19, col = "red", ylim = c(0, 1), xlab = "SELEX Round", cex = 4) # Fraction of true positives
points(1:4, vec2, type = "b", pch = 19, col = "blue", cex = 4) # Fraction of false negatives

```



# Plot comparison to HT-SELEX
```{r}
# Select Cycle
NKX2.5_PBM_Escores_PADIT$Selected_Cycle <- NKX2.5_PBM_Escores_PADIT$Cycle4

# Define Colours
NKX2.5_PBM_Escores_PADIT$Colour <- "black"
NKX2.5_PBM_Escores_PADIT$Colour[which(NKX2.5_PBM_Escores_PADIT$MPRAactivity == 1)] <- "red"
NKX2.5_PBM_Escores_PADIT$Colour[which(NKX2.5_PBM_Escores_PADIT$Selected_Cycle == 1)] <- "cyan3"
NKX2.5_PBM_Escores_PADIT_subset <- NKX2.5_PBM_Escores_PADIT[which(NKX2.5_PBM_Escores_PADIT$Median_baseMean > 5),]

# Plot -1
plot(NKX2.5_PBM_Escores_PADIT_subset$E.score[which(NKX2.5_PBM_Escores_PADIT_subset$Colour == "black")], 
     NKX2.5_PBM_Escores_PADIT_subset$Mean_log2FC[which(NKX2.5_PBM_Escores_PADIT_subset$Colour == "black")], 
     cex = 0.5, pch = 19, cex.axis = 2, cex.lab = 2,
     col = "black", 
     xlim = c(-0.45, 0.5), ylim = c(-0.5, 3.8), 
     xlab = "E-score", ylab = "PADIT-seq log2 (ALFA-NKX2.5 / No-DBD)")
points(NKX2.5_PBM_Escores_PADIT_subset$E.score[which(NKX2.5_PBM_Escores_PADIT_subset$Colour == "cyan3")], 
       NKX2.5_PBM_Escores_PADIT_subset$Mean_log2FC[which(NKX2.5_PBM_Escores_PADIT_subset$Colour == "cyan3")],
       cex = 0.5, pch = 19, col = "cyan3")
points(NKX2.5_PBM_Escores_PADIT_subset$E.score[which(NKX2.5_PBM_Escores_PADIT_subset$Colour == "red")], 
       NKX2.5_PBM_Escores_PADIT_subset$Mean_log2FC[which(NKX2.5_PBM_Escores_PADIT_subset$Colour == "red")],
       cex = 0.5, pch = 19, col = "red")
abline(h = 0, col = "red")
table(NKX2.5_PBM_Escores_PADIT_subset$Colour)

# Plot -2
plot(NKX2.5_PBM_Escores_PADIT_subset$E.score[which(NKX2.5_PBM_Escores_PADIT_subset$Colour == "black")], 
     NKX2.5_PBM_Escores_PADIT_subset$Mean_log2FC[which(NKX2.5_PBM_Escores_PADIT_subset$Colour == "black")], 
     cex = 0.5, pch = 19, cex.axis = 2, cex.lab = 2,
     col = "black", 
     xlim = c(-0.45, 0.5), ylim = c(-0.5, 3.8), 
     xlab = "E-score", ylab = "PADIT-seq log2 (ALFA-NKX2.5 / No-DBD)")
points(NKX2.5_PBM_Escores_PADIT_subset$E.score[which(NKX2.5_PBM_Escores_PADIT_subset$Colour != "black")], 
       NKX2.5_PBM_Escores_PADIT_subset$Mean_log2FC[which(NKX2.5_PBM_Escores_PADIT_subset$Colour != "black")],
       cex = 0.5, pch = 19, 
       col = NKX2.5_PBM_Escores_PADIT_subset$Colour[which(NKX2.5_PBM_Escores_PADIT_subset$Colour != "black")])
abline(h = 0, col = "red")
table(NKX2.5_PBM_Escores_PADIT_subset$Colour)

# Boxplot
boxplot(NKX2.5_PBM_Escores_PADIT$Mean_log2FC[which(NKX2.5_PBM_Escores_PADIT$Selected_Cycle == 0 & NKX2.5_PBM_Escores_PADIT$MPRAactivity == 1)],
        NKX2.5_PBM_Escores_PADIT$Mean_log2FC[which(NKX2.5_PBM_Escores_PADIT$Selected_Cycle == 1 & NKX2.5_PBM_Escores_PADIT$MPRAactivity == 1)],
        notch = TRUE, outline = FALSE, col = c("red", "cyan3"))
wilcox.test(NKX2.5_PBM_Escores_PADIT$Mean_log2FC[which(NKX2.5_PBM_Escores_PADIT$Selected_Cycle == 0 & NKX2.5_PBM_Escores_PADIT$MPRAactivity == 1)],
            NKX2.5_PBM_Escores_PADIT$Mean_log2FC[which(NKX2.5_PBM_Escores_PADIT$Selected_Cycle == 1 & NKX2.5_PBM_Escores_PADIT$MPRAactivity == 1)])

# Table
NKX2.5_PBM_Escores_PADIT$MPRAactivity[is.na(NKX2.5_PBM_Escores_PADIT$MPRAactivity)] <- 0
table(NKX2.5_PBM_Escores_PADIT$Selected_Cycle, NKX2.5_PBM_Escores_PADIT$MPRAactivity)


##########################
NKX2.5_PBM_Escores_PADIT$InteractionTerm <- interaction(NKX2.5_PBM_Escores_PADIT$Selected_Cycle, NKX2.5_PBM_Escores_PADIT$MPRAactivity)
boxplot(NKX2.5_PBM_Escores_PADIT$E.score ~ NKX2.5_PBM_Escores_PADIT$InteractionTerm,
        notch = TRUE, outline = FALSE, col = "yellow")
pairwise.wilcox.test(NKX2.5_PBM_Escores_PADIT$E.score, NKX2.5_PBM_Escores_PADIT$InteractionTerm)
table(NKX2.5_PBM_Escores_PADIT$InteractionTerm)

```


# compare to ProBound results
```{r}
# _NNNN
All8mers_1 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_NKX2-5/ProBound", sep = "/"), "All_8mers__NNNN_ProBound.txt", sep = "/"), header = FALSE)
colnames(All8mers_1) <- c("kmer", "rel_affinity1")

# N_NNNN
All8mers_2 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_NKX2-5/ProBound", sep = "/"), "All_8mers_N_NNN_ProBound.txt", sep = "/"), header = FALSE)
colnames(All8mers_2) <- c("kmer", "rel_affinity2")

# NN_NNN
All8mers_3 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_NKX2-5/ProBound", sep = "/"), "All_8mers_NN_NN_ProBound.txt", sep = "/"), header = FALSE)
colnames(All8mers_3) <- c("kmer", "rel_affinity3")

# NNN_N
All8mers_4 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_NKX2-5/ProBound", sep = "/"), "All_8mers_NNN_N_ProBound.txt", sep = "/"), header = FALSE)
colnames(All8mers_4) <- c("kmer", "rel_affinity4")

# NNNN_
All8mers_5 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_NKX2-5/ProBound", sep = "/"), "All_8mers_NNNN__ProBound.txt", sep = "/"), header = FALSE)
colnames(All8mers_5) <- c("kmer", "rel_affinity5")

### Merge
All8mers <- All8mers_1
All8mers$rel_affinity2 <- All8mers_2$rel_affinity2
All8mers$rel_affinity3 <- All8mers_3$rel_affinity3
All8mers$rel_affinity4 <- All8mers_4$rel_affinity4
All8mers$rel_affinity5 <- All8mers_5$rel_affinity5
All8mers$trimmed_kmer <- substr(All8mers$kmer, 1, 8)
All8mers$rel_affinity <- apply(All8mers[, paste("rel_affinity", 1:5, sep = "")], 1, max)
ProBound_results <- All8mers[, c("trimmed_kmer", "rel_affinity")]

# Merge
TEMP1 <- merge(NKX2.5_PBM_Escores_PADIT, ProBound_results, 
               by.x = "X8.mer", by.y = "trimmed_kmer")
TEMP2 <- merge(TEMP1, ProBound_results, 
               by.x = "X8.mer.1", by.y = "trimmed_kmer")
NKX2.5_PBM_Escores_PADIT_ProBound <- TEMP2
NKX2.5_PBM_Escores_PADIT_ProBound$log2_rel_affinity <- log2(apply(NKX2.5_PBM_Escores_PADIT_ProBound[, c("rel_affinity.x", "rel_affinity.y")], 1, max))

# Define threshold for log2_rel_affinity
log2_rel_affinity_threshold <- -5
NKX2.5_PBM_Escores_PADIT_ProBound$log2_rel_affinity_sig <- (NKX2.5_PBM_Escores_PADIT_ProBound$log2_rel_affinity > log2_rel_affinity_threshold)*1

# Scatter plot
NKX2.5_PBM_Escores_PADIT_ProBound$Colour <- "black"
NKX2.5_PBM_Escores_PADIT_ProBound$Colour[which(NKX2.5_PBM_Escores_PADIT_ProBound$MPRAactivity == 1)] <- "red"
NKX2.5_PBM_Escores_PADIT_ProBound$Colour[which(NKX2.5_PBM_Escores_PADIT_ProBound$MPRAactivity == 1 & NKX2.5_PBM_Escores_PADIT_ProBound$log2_rel_affinity_sig == 1)] <- "cyan3"
NKX2.5_PBM_Escores_PADIT_ProBound <- NKX2.5_PBM_Escores_PADIT_ProBound[which(NKX2.5_PBM_Escores_PADIT_ProBound$Median_baseMean > 15), ]
plot(NKX2.5_PBM_Escores_PADIT_ProBound$log2_rel_affinity[which(NKX2.5_PBM_Escores_PADIT_ProBound$Colour == "black")],
     NKX2.5_PBM_Escores_PADIT_ProBound$Mean_log2FC[which(NKX2.5_PBM_Escores_PADIT_ProBound$Colour == "black")], 
     pch = 19, col = NKX2.5_PBM_Escores_PADIT_ProBound$Colour[which(NKX2.5_PBM_Escores_PADIT_ProBound$Colour == "black")], xlim = c(-16, -0.75), ylim = c(-0.5, 3.8))
points(NKX2.5_PBM_Escores_PADIT_ProBound$log2_rel_affinity[which(NKX2.5_PBM_Escores_PADIT_ProBound$Colour != "black")],
     NKX2.5_PBM_Escores_PADIT_ProBound$Mean_log2FC[which(NKX2.5_PBM_Escores_PADIT_ProBound$Colour != "black")], 
     pch = 19, col = NKX2.5_PBM_Escores_PADIT_ProBound$Colour[which(NKX2.5_PBM_Escores_PADIT_ProBound$Colour != "black")])
abline(v = log2_rel_affinity_threshold, col = "blue")

# Boxplot
boxplot(NKX2.5_PBM_Escores_PADIT_ProBound$Mean_log2FC[which(NKX2.5_PBM_Escores_PADIT_ProBound$log2_rel_affinity_sig == 0 & NKX2.5_PBM_Escores_PADIT_ProBound$MPRAactivity == 1)], 
        NKX2.5_PBM_Escores_PADIT_ProBound$Mean_log2FC[which(NKX2.5_PBM_Escores_PADIT_ProBound$log2_rel_affinity_sig == 1 & NKX2.5_PBM_Escores_PADIT_ProBound$MPRAactivity == 1)], 
        notch = TRUE, outline = FALSE, col = c("red", "chartreuse4"))
wilcox.test(NKX2.5_PBM_Escores_PADIT_ProBound$Mean_log2FC[which(NKX2.5_PBM_Escores_PADIT_ProBound$log2_rel_affinity_sig == 0 & NKX2.5_PBM_Escores_PADIT_ProBound$MPRAactivity == 1)], 
        NKX2.5_PBM_Escores_PADIT_ProBound$Mean_log2FC[which(NKX2.5_PBM_Escores_PADIT_ProBound$log2_rel_affinity_sig == 1 & NKX2.5_PBM_Escores_PADIT_ProBound$MPRAactivity == 1)])
table(NKX2.5_PBM_Escores_PADIT_ProBound$log2_rel_affinity_sig, NKX2.5_PBM_Escores_PADIT_ProBound$MPRAactivity)

```


# compare to FIMO results
```{r}
# define colours
NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$Colour <- "black"
NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$Colour[which(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$MPRAactivity == 1)] <- "red"
NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$Colour[which(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$FIMO.p.value > -log10(0.005))] <- "cyan3"

# plot
plot(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$E.score[which(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$Colour == "black")],
     NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$Mean_log2FC[which(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$Colour == "black")], 
     cex = 0.5, pch = 19, col = NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$Colour[which(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$Colour == "black")], xlim = c(-0.45, 0.5), ylim = c(-0.5, 3.8))
points(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$E.score[which(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$Colour != "black")],
     NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$Mean_log2FC[which(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$Colour != "black")], 
     cex = 0.5, pch = 19, col = NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$Colour[which(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$Colour != "black")])
abline(h = 0, col = "red")

# boxplot
boxplot(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$Mean_log2FC[which(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$Colour == "red")],
        NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$Mean_log2FC[which(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$Colour == "cyan3" & NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$MPRAactivity == 1)], 
        col = c("red", "cyan3"), notch = TRUE, outline = FALSE)
table(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$Colour)
nrow(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO[which(NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$MPRAactivity == 1 & NKX2.5_PBM_Escores_PADIT_HTSELEX_ProBound_FIMO$Colour == "cyan3"), ])

```


