---
title: "R Notebook"
output: html_notebook
---
# Set Global Variables here

```{r}
# Please change the working directory
Working_dir <- "~/Desktop/AVATAR/PADIT-seq-Manuscript/Code_Availability/"

# Please be sure to install these libraries
library(pheatmap); library(ggplot2); library(DESeq2); library(ggrepel); library("stringr")

# FDR cutoff (do not change)
Cutoff_Value <- 0.05
```



# Obtain EGR1 9-mer PADIT-seq log2foldchange values from 10-mer data
# Caution: This is going to take a while (~7 hours) (Sorry - I only had to do this once so I did not bother optimizing the code)
```{r}
# Read ZIF268 PADIT-seq data
dds_results_ZIF268_df <- read.table(paste(paste(Working_dir, "Output_Files", sep = "/"), "dds_results_ZIF268_df.txt", sep = "/"), header = TRUE)
dds_results_ZIF268_df$TFBS <- rownames(dds_results_ZIF268_df)

# Read and format ZIF268 PBM data
V1 <- read.table(paste(paste(Working_dir, "Input_Files/PBM_data_Egr1", sep = "/"), "Zif268_v1_kf0.5_9mers_111111111.txt", sep = "/"), header = TRUE)
V2 <- read.table(paste(paste(Working_dir, "Input_Files/PBM_data_Egr1", sep = "/"), "Zif268_v2_kf0.5_9mers_111111111.txt", sep = "/"), header = TRUE)
TEMP <- merge(V1, V2, by = "X9.mer")
TEMP$E.score <- apply(TEMP[, c("E.score.x", "E.score.y")], 1, max)
TEMP$Z.score <- apply(TEMP[, c("Z.score.x", "Z.score.y")], 1, min)
ZIF268_PBM_Escores <- TEMP[, c("X9.mer", "X9.mer.1.x", "E.score", "Z.score")]; rm(TEMP)
colnames(ZIF268_PBM_Escores) <- c("X9.mer", "X9.mer.1", "E.score", "Z.score")

# 
for(k in 0:1) # The 2 9-mers overlapping each 10-mer
{
  #
  ZIF268_PBM_Escores_PADIT <- data.frame()
  for(i in 1:nrow(ZIF268_PBM_Escores)) # For each register, calculate the median 9-mer scores
  {
    Current_8mers <- ZIF268_PBM_Escores[i,]
  
    Fwd <- dds_results_ZIF268_df[which(substr(dds_results_ZIF268_df$TFBS, k+1, k+9) == Current_8mers$X9.mer[1]),]
    Fwd.tmp <- Fwd[order(Fwd$log2FoldChange, decreasing = TRUE),]
    Fwd <- Fwd.tmp; rm(Fwd.tmp)
    if(nrow(Fwd) > 0)
    {
      Fwd_subset <- Fwd[ceiling(nrow(Fwd)/2), c("log2FoldChange", "padj", "MPRAactivity")]
    }
    else
    {
      Fwd_subset <- as.data.frame(t(c(-100, 1, 0)))
      colnames(Fwd_subset) <- c("log2FoldChange", "padj", "MPRAactivity")
    }
  
    Rev <- dds_results_ZIF268_df[which(substr(dds_results_ZIF268_df$TFBS, k+1, k+9) == Current_8mers$X9.mer.1[1]),]
    Rev.tmp <- Rev[order(Rev$log2FoldChange, decreasing = TRUE),]
    Rev <- Rev.tmp; rm(Rev.tmp)
    if(nrow(Rev) > 0)
    {
      Rev_subset <- Rev[ceiling(nrow(Rev)/2), c("log2FoldChange", "padj", "MPRAactivity")]
    }
    else
    {
      Rev_subset <- as.data.frame(t(c(-100, 1, 0)))
      colnames(Rev_subset) <- c("log2FoldChange", "padj", "MPRAactivity")
    }
  
    if((Fwd_subset$log2FoldChange >= Rev_subset$log2FoldChange) | (nrow(Rev_subset) == 0))
    {
      Current_8mers <- cbind(Current_8mers, Fwd_subset)
    }
    if((Fwd_subset$log2FoldChange < Rev_subset$log2FoldChange) | (nrow(Fwd_subset) == 0))
    {
      Current_8mers <- cbind(Current_8mers, Rev_subset)
    }
  
    ZIF268_PBM_Escores_PADIT <- rbind(ZIF268_PBM_Escores_PADIT, Current_8mers)
  
    # remove all the variable in current iteration
    variables_to_remove = c("Current_8mers", "Fwd", "Fwd_subset", "Rev", "Rev_subset")
    for (var_name in variables_to_remove)
    {
      if (exists(var_name))
      {
        rm(list=var_name)
      }
    }
  }
  
  # Store the files
  if(k == 0){ write.table(ZIF268_PBM_Escores_PADIT, file = paste(paste(Working_dir, "Output_Files", sep = "/"), "ZIF268_all9mers_1_9_median.txt", sep = "/"), col.names = TRUE, row.names = FALSE, quote = FALSE, sep = "\t") }
  if(k == 1){ write.table(ZIF268_PBM_Escores_PADIT, file = paste(paste(Working_dir, "Output_Files", sep = "/"), "ZIF268_all9mers_2_10_median.txt", sep = "/"), col.names = TRUE, row.names = FALSE, quote = FALSE, sep = "\t") }
}

```


# Plot comparison to PBM E-scores
```{r}
# Read and format ZIF268 PBM data
V1 <- read.table(paste(paste(Working_dir, "Input_Files/PBM_data_Egr1", sep = "/"), "Zif268_v1_kf0.5_9mers_111111111.txt", sep = "/"), header = TRUE)
V2 <- read.table(paste(paste(Working_dir, "Input_Files/PBM_data_Egr1", sep = "/"), "Zif268_v2_kf0.5_9mers_111111111.txt", sep = "/"), header = TRUE)
TEMP <- merge(V1, V2, by = "X9.mer")
TEMP$E.score <- apply(TEMP[, c("E.score.x", "E.score.y")], 1, max)
TEMP$Z.score <- apply(TEMP[, c("Z.score.x", "Z.score.y")], 1, min)
ZIF268_PBM_Escores <- TEMP[, c("X9.mer", "X9.mer.1.x", "E.score", "Z.score")]; rm(TEMP)
colnames(ZIF268_PBM_Escores) <- c("X9.mer", "X9.mer.1", "E.score", "Z.score")

# Read PADIT-seq log2foldchanges
Register_1_9 <- read.table(paste(paste(Working_dir, "Output_Files", sep = "/"), "ZIF268_all9mers_1_9_median.txt", sep = "/"), header = TRUE)
Register_2_10 <- read.table(paste(paste(Working_dir, "Output_Files", sep = "/"), "ZIF268_all9mers_2_10_median.txt", sep = "/"), header = TRUE)

# Re-define MPRAactivity
Register_1_9$MPRAactivity <- (Register_1_9$log2FoldChange > 0 & Register_1_9$padj < Cutoff_Value)*1
Register_2_10$MPRAactivity <- (Register_2_10$log2FoldChange > 0 & Register_2_10$padj < Cutoff_Value)*1

# Number of red points?
table(Register_1_9$MPRAactivity)
table(Register_2_10$MPRAactivity)

# Fraction of red points?
sum((Register_1_9$MPRAactivity == 1)*1)/nrow(Register_1_9)
sum((Register_2_10$MPRAactivity == 1)*1)/nrow(Register_2_10)

# Format
colnames(Register_1_9) <- paste(colnames(Register_1_9), "1_9", sep = "_")
colnames(Register_2_10) <- paste(colnames(Register_2_10), "2_10", sep = "_")
TEMP1 <- merge(Register_1_9, Register_2_10, 
               by.x = "X9.mer_1_9", by.y = "X9.mer_2_10")
ZIF268_PBM_Escores_PADIT <- TEMP1; rm(TEMP1)
ZIF268_PBM_Escores_PADIT$Mean_log2FC <- apply(ZIF268_PBM_Escores_PADIT[,c("log2FoldChange_1_9", "log2FoldChange_2_10")], 1, min)
ZIF268_PBM_Escores_PADIT$MPRAactivity <- apply(ZIF268_PBM_Escores_PADIT[,c("MPRAactivity_1_9", "MPRAactivity_2_10")], 1, min)

# Plot
TEMP <- merge(ZIF268_PBM_Escores, ZIF268_PBM_Escores_PADIT, by.x = "X9.mer", by.y = "X9.mer_1_9")
ZIF268_PBM_Escores_PADIT_subset <- TEMP
ZIF268_PBM_Escores_PADIT_subset$Colour <- "black"
ZIF268_PBM_Escores_PADIT_subset$Colour[which(ZIF268_PBM_Escores_PADIT_subset$MPRAactivity == 1)] <- "red"
plot(ZIF268_PBM_Escores_PADIT_subset$E.score[which(ZIF268_PBM_Escores_PADIT_subset$Colour == "black")], 
     ZIF268_PBM_Escores_PADIT_subset$Mean_log2FC[which(ZIF268_PBM_Escores_PADIT_subset$Colour == "black")], 
     cex = 0.4, pch = 19, cex.axis = 2, cex.lab = 2,
     col = "black", 
     xlim = c(-0.5, 0.5), ylim = c(-0.5, 2.8), 
     xlab = "E-score", ylab = "PADIT-seq log2 (ALFA-ZIF268 / No-DBD)")
points(ZIF268_PBM_Escores_PADIT_subset$E.score[which(ZIF268_PBM_Escores_PADIT_subset$Colour == "red")], 
       ZIF268_PBM_Escores_PADIT_subset$Mean_log2FC[which(ZIF268_PBM_Escores_PADIT_subset$Colour == "red")], 
     cex = 0.4, pch = 19,
     col = "red")
abline(h = 0, col = "red")
abline(v = 0.45, col = "red")
table(ZIF268_PBM_Escores_PADIT_subset$Colour)

################################################################# AUC analysis
library("DescTools")
escores_thresholds <- seq(-0.5, 0.5, by = 0.001)
fraction_red <- vector()
fraction_black <- vector()
for(i in 1:length(escores_thresholds))
{
  ZIF268_PBM_Escores_PADIT$PBM_escore_threshold <- (ZIF268_PBM_Escores_PADIT$E.score_1_9 > escores_thresholds[i])*1
  fraction_red[i] <- nrow(ZIF268_PBM_Escores_PADIT[which(ZIF268_PBM_Escores_PADIT$MPRAactivity == 1 & ZIF268_PBM_Escores_PADIT$PBM_escore_threshold == 1),])
  fraction_black[i] <- nrow(ZIF268_PBM_Escores_PADIT[which(ZIF268_PBM_Escores_PADIT$MPRAactivity != 1 & ZIF268_PBM_Escores_PADIT$PBM_escore_threshold == 1),])
}

# Plot AUC curve
ZIF268_PBM_Escores_PADIT$MPRAactivity[is.na(ZIF268_PBM_Escores_PADIT$MPRAactivity)] <- 0
plot(fraction_black/(nrow(ZIF268_PBM_Escores_PADIT) - sum(ZIF268_PBM_Escores_PADIT$MPRAactivity)), 
     fraction_red/sum(ZIF268_PBM_Escores_PADIT$MPRAactivity), 
     type = "b")

# Caluclate AUC
AUC(fraction_black/(nrow(ZIF268_PBM_Escores_PADIT) - sum(ZIF268_PBM_Escores_PADIT$MPRAactivity)), 
    fraction_red/sum(ZIF268_PBM_Escores_PADIT$MPRAactivity)) 

# Obtain best e-score threshold
escores_thresholds_DF <- cbind(escores_thresholds, 
                               fraction_black/(nrow(ZIF268_PBM_Escores_PADIT) - sum(ZIF268_PBM_Escores_PADIT$MPRAactivity)),
                               fraction_red/sum(ZIF268_PBM_Escores_PADIT$MPRAactivity))
escores_thresholds_DF <- as.data.frame(escores_thresholds_DF)
colnames(escores_thresholds_DF) <- c("escores_thresholds", "false_positives", "true_positives")
View(escores_thresholds_DF[which(escores_thresholds_DF$true_positives > 0.7),])

```

# Specificity versus Sensitivity of HT-SELEX data
```{r}
# Observed versus Expected threshold
ratio_threshold <- 3

# Define the active 8-mers
ZIF268_PBM_Escores_PADIT_subset_sig9mers <- c(ZIF268_PBM_Escores_PADIT_subset$X9.mer[which(ZIF268_PBM_Escores_PADIT_subset$MPRAactivity == 1)], 
                                              ZIF268_PBM_Escores_PADIT_subset$X9.mer.1[which(ZIF268_PBM_Escores_PADIT_subset$MPRAactivity == 1)])
ZIF268_PBM_Escores_PADIT_subset_sig9mers <- unique(ZIF268_PBM_Escores_PADIT_subset_sig9mers)

# Read HT-SELEX enriched 8-mers
table_1 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_EGR1", sep = "/"), "EGR1_HT-SELEX_Cycle1_enriched_9mers.txt", sep = "/"), header = TRUE)
table_2 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_EGR1", sep = "/"), "EGR1_HT-SELEX_Cycle2_enriched_9mers.txt", sep = "/"), header = TRUE)
table_3 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_EGR1", sep = "/"), "EGR1_HT-SELEX_Cycle3_enriched_9mers.txt", sep = "/"), header = TRUE)
table_4 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_EGR1", sep = "/"), "EGR1_HT-SELEX_Cycle4_enriched_9mers.txt", sep = "/"), header = TRUE)

# filter
table_1 <- table_1[which(table_1$ObservedCount/table_1$ExpectedCount > ratio_threshold),]
table_2 <- table_2[which(table_2$ObservedCount/table_2$ExpectedCount > ratio_threshold),]
table_3 <- table_3[which(table_3$ObservedCount/table_3$ExpectedCount > ratio_threshold),]
table_4 <- table_4[which(table_4$ObservedCount/table_4$ExpectedCount > ratio_threshold),]

# Add relevant columns
ZIF268_PBM_Escores_PADIT_subset$Cycle1 <- (ZIF268_PBM_Escores_PADIT_subset$X9.mer %in% table_1$Kmer | ZIF268_PBM_Escores_PADIT_subset$X9.mer.1 %in% table_1$Kmer)*1 
ZIF268_PBM_Escores_PADIT_subset$Cycle2 <- (ZIF268_PBM_Escores_PADIT_subset$X9.mer %in% table_2$Kmer | ZIF268_PBM_Escores_PADIT_subset$X9.mer.1 %in% table_2$Kmer)*1 
ZIF268_PBM_Escores_PADIT_subset$Cycle3 <- (ZIF268_PBM_Escores_PADIT_subset$X9.mer %in% table_3$Kmer | ZIF268_PBM_Escores_PADIT_subset$X9.mer.1 %in% table_3$Kmer)*1 
ZIF268_PBM_Escores_PADIT_subset$Cycle4 <- (ZIF268_PBM_Escores_PADIT_subset$X9.mer %in% table_4$Kmer | ZIF268_PBM_Escores_PADIT_subset$X9.mer.1 %in% table_4$Kmer)*1 

# Number of rows
num_enriched_HTSELEX <- c(sum(ZIF268_PBM_Escores_PADIT_subset$Cycle1),
                          sum(ZIF268_PBM_Escores_PADIT_subset$Cycle2),
                          sum(ZIF268_PBM_Escores_PADIT_subset$Cycle3),
                          sum(ZIF268_PBM_Escores_PADIT_subset$Cycle4))

# Specificity (red)
vec1 <- c(nrow(ZIF268_PBM_Escores_PADIT_subset[which(ZIF268_PBM_Escores_PADIT_subset$Cycle1 == 1 & ZIF268_PBM_Escores_PADIT_subset$MPRAactivity == 1),]),
          nrow(ZIF268_PBM_Escores_PADIT_subset[which(ZIF268_PBM_Escores_PADIT_subset$Cycle2 == 1 & ZIF268_PBM_Escores_PADIT_subset$MPRAactivity == 1),]),
          nrow(ZIF268_PBM_Escores_PADIT_subset[which(ZIF268_PBM_Escores_PADIT_subset$Cycle3 == 1 & ZIF268_PBM_Escores_PADIT_subset$MPRAactivity == 1),]),
          nrow(ZIF268_PBM_Escores_PADIT_subset[which(ZIF268_PBM_Escores_PADIT_subset$Cycle4 == 1 & ZIF268_PBM_Escores_PADIT_subset$MPRAactivity == 1),]))
vec1 <- vec1/num_enriched_HTSELEX

# Sensitivity (blue)
vec2 <- c(nrow(ZIF268_PBM_Escores_PADIT_subset[which(ZIF268_PBM_Escores_PADIT_subset$Cycle1 == 1 & ZIF268_PBM_Escores_PADIT_subset$MPRAactivity == 1),]),
          nrow(ZIF268_PBM_Escores_PADIT_subset[which(ZIF268_PBM_Escores_PADIT_subset$Cycle2 == 1 & ZIF268_PBM_Escores_PADIT_subset$MPRAactivity == 1),]),
          nrow(ZIF268_PBM_Escores_PADIT_subset[which(ZIF268_PBM_Escores_PADIT_subset$Cycle3 == 1 & ZIF268_PBM_Escores_PADIT_subset$MPRAactivity == 1),]),
          nrow(ZIF268_PBM_Escores_PADIT_subset[which(ZIF268_PBM_Escores_PADIT_subset$Cycle4 == 1 & ZIF268_PBM_Escores_PADIT_subset$MPRAactivity == 1),]))
vec2 <- vec2/length(ZIF268_PBM_Escores_PADIT_subset_sig9mers)

# 
plot(1:4, vec1, type = "b", pch = 19, col = "red", ylim = c(0, 1), xlab = "SELEX Round", cex = 4) # Fraction of true positives
points(1:4, vec2, type = "b", pch = 19, col = "blue", cex = 4) # Fraction of false negatives
```



# Plot comparison to HT-SELEX
```{r}
# Observed versus Expected threshold
ratio_threshold <- 3

# Select Cycle
ZIF268_PBM_Escores_PADIT_subset$Selected_Cycle <- ZIF268_PBM_Escores_PADIT_subset$Cycle3

# Plot - 1
ZIF268_PBM_Escores_PADIT_subset$Colour <- "black"
ZIF268_PBM_Escores_PADIT_subset$Colour[which(ZIF268_PBM_Escores_PADIT_subset$MPRAactivity == 1)] <- "red"
ZIF268_PBM_Escores_PADIT_subset$Colour[which(ZIF268_PBM_Escores_PADIT_subset$Selected_Cycle == 1)] <- "blue"
plot(ZIF268_PBM_Escores_PADIT_subset$E.score[which(ZIF268_PBM_Escores_PADIT_subset$Colour == "black")], 
     ZIF268_PBM_Escores_PADIT_subset$Mean_log2FC[which(ZIF268_PBM_Escores_PADIT_subset$Colour == "black")], 
     cex = 0.4, pch = 19, cex.axis = 2, cex.lab = 2,
     col = "black", 
     xlim = c(-0.5, 0.5), ylim = c(-0.5, 2.8), 
     xlab = "E-score", ylab = "PADIT-seq log2 (ALFA-ZIF268 / No-DBD)")
points(ZIF268_PBM_Escores_PADIT_subset$E.score[which(ZIF268_PBM_Escores_PADIT_subset$Colour == "red")], 
       ZIF268_PBM_Escores_PADIT_subset$Mean_log2FC[which(ZIF268_PBM_Escores_PADIT_subset$Colour == "red")], 
     cex = 0.4, pch = 19,
     col = "red")
points(ZIF268_PBM_Escores_PADIT_subset$E.score[which(ZIF268_PBM_Escores_PADIT_subset$Colour == "blue")],
       ZIF268_PBM_Escores_PADIT_subset$Mean_log2FC[which(ZIF268_PBM_Escores_PADIT_subset$Colour == "blue")],
     cex = 0.4, pch = 19,
     col = "blue")
abline(h = 0, col = "red")
table(ZIF268_PBM_Escores_PADIT_subset$Colour)

# Plot - 2
plot(ZIF268_PBM_Escores_PADIT_subset$E.score[which(ZIF268_PBM_Escores_PADIT_subset$Colour == "black")], 
     ZIF268_PBM_Escores_PADIT_subset$Mean_log2FC[which(ZIF268_PBM_Escores_PADIT_subset$Colour == "black")], 
     cex = 0.4, pch = 19, cex.axis = 2, cex.lab = 2,
     col = "black", 
     xlim = c(-0.5, 0.5), ylim = c(-0.5, 2.8), 
     xlab = "E-score", ylab = "PADIT-seq log2 (ALFA-ZIF268 / No-DBD)")
points(ZIF268_PBM_Escores_PADIT_subset$E.score[which(ZIF268_PBM_Escores_PADIT_subset$Colour != "black")],
       ZIF268_PBM_Escores_PADIT_subset$Mean_log2FC[which(ZIF268_PBM_Escores_PADIT_subset$Colour != "black")],
     cex = 0.4, pch = 19,
     col = ZIF268_PBM_Escores_PADIT_subset$Colour[which(ZIF268_PBM_Escores_PADIT_subset$Colour != "black")])
abline(h = 0, col = "red")
table(ZIF268_PBM_Escores_PADIT_subset$Colour)

# Boxplot
boxplot(ZIF268_PBM_Escores_PADIT_subset$Mean_log2FC[which(ZIF268_PBM_Escores_PADIT_subset$Selected_Cycle == 0 & ZIF268_PBM_Escores_PADIT_subset$MPRAactivity == 1)],
        ZIF268_PBM_Escores_PADIT_subset$Mean_log2FC[which(ZIF268_PBM_Escores_PADIT_subset$Selected_Cycle == 1 & ZIF268_PBM_Escores_PADIT_subset$MPRAactivity == 1)],
        notch = TRUE, outline = FALSE, col = c("red", "blue"))
wilcox.test(ZIF268_PBM_Escores_PADIT_subset$Mean_log2FC[which(ZIF268_PBM_Escores_PADIT_subset$Selected_Cycle == 0 & ZIF268_PBM_Escores_PADIT_subset$MPRAactivity == 1)],
            ZIF268_PBM_Escores_PADIT_subset$Mean_log2FC[which(ZIF268_PBM_Escores_PADIT_subset$Selected_Cycle == 1 & ZIF268_PBM_Escores_PADIT_subset$MPRAactivity == 1)])

# Table
ZIF268_PBM_Escores_PADIT_subset$MPRAactivity[is.na(ZIF268_PBM_Escores_PADIT_subset$MPRAactivity)] <- 0
table(ZIF268_PBM_Escores_PADIT_subset$Selected_Cycle, ZIF268_PBM_Escores_PADIT_subset$MPRAactivity)

##########################
ZIF268_PBM_Escores_PADIT_subset$InteractionTerm <- interaction(ZIF268_PBM_Escores_PADIT_subset$Selected_Cycle, ZIF268_PBM_Escores_PADIT_subset$MPRAactivity)
boxplot(ZIF268_PBM_Escores_PADIT_subset$E.score ~ ZIF268_PBM_Escores_PADIT_subset$InteractionTerm,
        notch = TRUE, outline = FALSE, col = "yellow")
pairwise.wilcox.test(ZIF268_PBM_Escores_PADIT_subset$E.score, ZIF268_PBM_Escores_PADIT_subset$InteractionTerm)
table(ZIF268_PBM_Escores_PADIT_subset$InteractionTerm)

```





# Compare PADIT-seq and MITOMI-derived Kd
```{r}
# Read MITOMI KD data
MITOMI_KD <- read.table(paste(paste(Working_dir, "Input_Files", sep = "/"), "ZIF268_MITOMI_Kd_kmer9.txt", sep = "/"), header = TRUE)

# Merge
TEMP1 <- merge(MITOMI_KD, ZIF268_PBM_Escores_PADIT, by.x = "kmer9", by.y = "X9.mer_1_9")[, c("kmer9", "MITOMI_Kd", "Mean_log2FC", "MPRAactivity")]
TEMP2 <- merge(MITOMI_KD, ZIF268_PBM_Escores_PADIT, by.x = "kmer9", by.y = "X9.mer.1_1_9")[, c("kmer9", "MITOMI_Kd", "Mean_log2FC", "MPRAactivity")]
dds_results_ZIF268_MITOMI_df <- rbind(TEMP1, TEMP2)

# plot
dds_results_ZIF268_MITOMI_df$Colour <- "black"
dds_results_ZIF268_MITOMI_df$Colour[which(dds_results_ZIF268_MITOMI_df$MPRAactivity == 1)] <- "red"

# plot with best fit line
plot(-log10(dds_results_ZIF268_MITOMI_df$MITOMI_Kd), 
     dds_results_ZIF268_MITOMI_df$Mean_log2FC, 
     pch = 19, cex = 2, col = dds_results_ZIF268_MITOMI_df$Colour,
     xlab = "-log10(MITOMI KD)", ylab = "PADIT-seq log2FC")

# Correlation
cor.test(-log10(dds_results_ZIF268_MITOMI_df$MITOMI_Kd), 
         dds_results_ZIF268_MITOMI_df$Mean_log2FC, method = "pearson")
cor.test(-log10(dds_results_ZIF268_MITOMI_df$MITOMI_Kd), 
         dds_results_ZIF268_MITOMI_df$Mean_log2FC, method = "spearman")

```



# compare to ProBound results
```{r}
# _NNNNN
All9mers_1 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_EGR1/ProBound", sep = "/"), "All_9mers__NNNNN_ProBound.txt", sep = "/"), header = FALSE)
colnames(All9mers_1) <- c("kmer", "rel_affinity1")

# N_NNNN
All9mers_2 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_EGR1/ProBound", sep = "/"), "All_9mers_N_NNNN_ProBound.txt", sep = "/"), header = FALSE)
colnames(All9mers_2) <- c("kmer", "rel_affinity2")

# NN_NNN
All9mers_3 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_EGR1/ProBound", sep = "/"), "All_9mers_NN_NNN_ProBound.txt", sep = "/"), header = FALSE)
colnames(All9mers_3) <- c("kmer", "rel_affinity3")

# NNN_NN
All9mers_4 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_EGR1/ProBound", sep = "/"), "All_9mers_NNN_NN_ProBound.txt", sep = "/"), header = FALSE)
colnames(All9mers_4) <- c("kmer", "rel_affinity4")

# NNNN_N
All9mers_5 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_EGR1/ProBound", sep = "/"), "All_9mers_NNNN_N_ProBound.txt", sep = "/"), header = FALSE)
colnames(All9mers_5) <- c("kmer", "rel_affinity5")

# NNNNN_
All9mers_6 <- read.table(paste(paste(Working_dir, "Input_Files/HT-SELEX_data_EGR1/ProBound", sep = "/"), "All_9mers_NNNNN__ProBound.txt", sep = "/"), header = FALSE)
colnames(All9mers_6) <- c("kmer", "rel_affinity6")

### Merge
All9mers <- All9mers_1
All9mers$rel_affinity2 <- All9mers_2$rel_affinity2
All9mers$rel_affinity3 <- All9mers_3$rel_affinity3
All9mers$rel_affinity4 <- All9mers_4$rel_affinity4
All9mers$rel_affinity5 <- All9mers_5$rel_affinity5
All9mers$rel_affinity6 <- All9mers_6$rel_affinity6
All9mers$trimmed_kmer <- substr(All9mers$kmer, 1, 9)
All9mers$rel_affinity <- apply(All9mers[, paste("rel_affinity", 1:6, sep = "")], 1, max)
ProBound_results <- All9mers[, c("trimmed_kmer", "rel_affinity")]

# Merge
TEMP1 <- merge(ZIF268_PBM_Escores_PADIT_subset, ProBound_results, 
               by.x = "X9.mer", by.y = "trimmed_kmer")
TEMP2 <- merge(TEMP1, ProBound_results, 
               by.x = "X9.mer.1", by.y = "trimmed_kmer")
ZIF268_PBM_Escores_PADIT_subset_ProBound <- TEMP2
ZIF268_PBM_Escores_PADIT_subset_ProBound$log2_rel_affinity <- log2(apply(ZIF268_PBM_Escores_PADIT_subset_ProBound[, c("rel_affinity.x", "rel_affinity.y")], 1, max))

# Define threshold for log2_rel_affinity
log2_rel_affinity_threshold <- -5
ZIF268_PBM_Escores_PADIT_subset_ProBound$log2_rel_affinity_sig <- (ZIF268_PBM_Escores_PADIT_subset_ProBound$log2_rel_affinity > log2_rel_affinity_threshold)*1

# Scatter plot 
ZIF268_PBM_Escores_PADIT_subset_ProBound$Colour <- "black"
ZIF268_PBM_Escores_PADIT_subset_ProBound$Colour[which(ZIF268_PBM_Escores_PADIT_subset_ProBound$MPRAactivity == 1)] <- "red"
plot(ZIF268_PBM_Escores_PADIT_subset_ProBound$log2_rel_affinity,
     ZIF268_PBM_Escores_PADIT_subset_ProBound$Mean_log2FC, 
     pch = 19, col = ZIF268_PBM_Escores_PADIT_subset_ProBound$Colour, 
     ylim = c(-0.6, 3))
abline(v = log2_rel_affinity_threshold, col = "blue")

# Boxplot
boxplot(ZIF268_PBM_Escores_PADIT_subset_ProBound$Mean_log2FC[which(ZIF268_PBM_Escores_PADIT_subset_ProBound$log2_rel_affinity_sig == 0 & ZIF268_PBM_Escores_PADIT_subset_ProBound$MPRAactivity == 1)], 
        ZIF268_PBM_Escores_PADIT_subset_ProBound$Mean_log2FC[which(ZIF268_PBM_Escores_PADIT_subset_ProBound$log2_rel_affinity_sig == 1 & ZIF268_PBM_Escores_PADIT_subset_ProBound$MPRAactivity == 1)], 
        notch = TRUE, outline = FALSE, col = c("red", "blue"))
wilcox.test(ZIF268_PBM_Escores_PADIT_subset_ProBound$Mean_log2FC[which(ZIF268_PBM_Escores_PADIT_subset_ProBound$log2_rel_affinity_sig == 0 & ZIF268_PBM_Escores_PADIT_subset_ProBound$MPRAactivity == 1)], 
        ZIF268_PBM_Escores_PADIT_subset_ProBound$Mean_log2FC[which(ZIF268_PBM_Escores_PADIT_subset_ProBound$log2_rel_affinity_sig == 1 & ZIF268_PBM_Escores_PADIT_subset_ProBound$MPRAactivity == 1)])
table(ZIF268_PBM_Escores_PADIT_subset_ProBound$log2_rel_affinity_sig, ZIF268_PBM_Escores_PADIT_subset_ProBound$MPRAactivity)

```






# AUROC analysis
```{r}
library("DescTools")

################################################################# AUC analysis PBM
escores_thresholds <- seq(-0.5, 0.5, by = 0.001)
fraction_red <- vector()
fraction_black <- vector()
for(i in 1:length(escores_thresholds))
{
  ZIF268_PBM_Escores_PADIT$PBM_escore_threshold <- (ZIF268_PBM_Escores_PADIT$E.score_1_9 > escores_thresholds[i])*1
  fraction_red[i] <- nrow(ZIF268_PBM_Escores_PADIT[which(ZIF268_PBM_Escores_PADIT$MPRAactivity == 1 & ZIF268_PBM_Escores_PADIT$PBM_escore_threshold == 1),])
  fraction_black[i] <- nrow(ZIF268_PBM_Escores_PADIT[which(ZIF268_PBM_Escores_PADIT$MPRAactivity != 1 & ZIF268_PBM_Escores_PADIT$PBM_escore_threshold == 1),])
}

# Plot AUC curve
ZIF268_PBM_Escores_PADIT$MPRAactivity[is.na(ZIF268_PBM_Escores_PADIT$MPRAactivity)] <- 0
plot(fraction_black/(nrow(ZIF268_PBM_Escores_PADIT) - sum(ZIF268_PBM_Escores_PADIT$MPRAactivity)), 
     fraction_red/sum(ZIF268_PBM_Escores_PADIT$MPRAactivity), 
     type = "l", pch = 19, col = "green")
abline(a = 0, b = 1, col = "black")

# Caluclate AUC
AUC(fraction_black/(nrow(ZIF268_PBM_Escores_PADIT) - sum(ZIF268_PBM_Escores_PADIT$MPRAactivity)), 
    fraction_red/sum(ZIF268_PBM_Escores_PADIT$MPRAactivity)) 

################################################################# AUC analysis ProBound
escores_thresholds <- seq(min(ZIF268_PBM_Escores_PADIT_subset_ProBound$log2_rel_affinity), 
                          max(ZIF268_PBM_Escores_PADIT_subset_ProBound$log2_rel_affinity), 
                          by = 0.1)
fraction_red <- vector()
fraction_black <- vector()
for(i in 1:length(escores_thresholds))
{
  ZIF268_PBM_Escores_PADIT_subset_ProBound$PBM_escore_threshold <- (ZIF268_PBM_Escores_PADIT_subset_ProBound$log2_rel_affinity > escores_thresholds[i])*1
  fraction_red[i] <- nrow(ZIF268_PBM_Escores_PADIT_subset_ProBound[which(ZIF268_PBM_Escores_PADIT_subset_ProBound$MPRAactivity == 1 & ZIF268_PBM_Escores_PADIT_subset_ProBound$PBM_escore_threshold == 1),])
  fraction_black[i] <- nrow(ZIF268_PBM_Escores_PADIT_subset_ProBound[which(ZIF268_PBM_Escores_PADIT_subset_ProBound$MPRAactivity != 1 & ZIF268_PBM_Escores_PADIT_subset_ProBound$PBM_escore_threshold == 1),])
}

# Plot AUC curve
ZIF268_PBM_Escores_PADIT_subset_ProBound$MPRAactivity[is.na(ZIF268_PBM_Escores_PADIT_subset_ProBound$MPRAactivity)] <- 0
points(fraction_black/(nrow(ZIF268_PBM_Escores_PADIT_subset_ProBound) - sum(ZIF268_PBM_Escores_PADIT_subset_ProBound$MPRAactivity)), 
     fraction_red/sum(ZIF268_PBM_Escores_PADIT_subset_ProBound$MPRAactivity), 
     type = "l", pch = 19, col = "blue")

# Caluclate AUC
AUC(fraction_black/(nrow(ZIF268_PBM_Escores_PADIT_subset_ProBound) - sum(ZIF268_PBM_Escores_PADIT_subset_ProBound$MPRAactivity)), 
    fraction_red/sum(ZIF268_PBM_Escores_PADIT_subset_ProBound$MPRAactivity)) 


```


